---
title: "NBA Spatial Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NBA Spatial Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# NBA spatial data

Spatial events are currently supported for NBA via ESPN summaries and NBA Stats
shot chart / play-by-play data.

## ESPN events (x_unit / y_unit in [0,1])

```{r, eval=FALSE}
library(spatialSportsR)

tables <- parse_raw(
  league = "nba",
  season = 2026,
  source = "espn",
  season_type = "regular",
  raw_dir = "data/raw"
)

events <- tables$events
head(events)
```

## NBA Stats shots

```{r, eval=FALSE}
tables <- parse_raw(
  league = "nba",
  season = 2026,
  source = "nba_stats",
  season_type = "Regular Season",
  raw_dir = "data/raw"
)

shots <- tables$shots
head(shots)
```

## Notes

- `events$x_unit` / `events$y_unit` are normalized to `[0,1]`.
- NBA Stats `shots` includes `event_num` or `shot_id` for uniqueness.

## NHL (planned)

NHL spatial parsing is planned but not implemented yet. This vignette will be
expanded once the NHL source adapter is complete.
